The Journey from Wild to Textbook Data: A Case Study from the National Longitudinal Survey of Youth

### 2021-09-16 paper/paper.Rmd

```{r setup, echo = FALSE, cache = FALSE, include = FALSE}
library(knitr)
opts_chunk$set(echo = FALSE, warning = FALSE, 
               message = FALSE,
               cache = TRUE, 
               cache.path = "paper_cache/",
               fig.retina = 2,
               fig.path = "figures/",
               comment = "#>",
               fig.align = 'center')

@@

\begin{tcolorbox}[width=\textwidth,
                  boxsep=5pt,
                  left=5pt,
                  right=5pt,
                  top=5pt,
                  ]
Education, Training and Achievement Scores

@@

Employment

@@

Household, Geography and Contextual Variables

>>>>

```{r setup, echo = FALSE, cache = FALSE, include = FALSE}
library(knitr)
opts_chunk$set(echo = FALSE, warning = FALSE, 
               message = FALSE,
               cache = TRUE, 
               cache.path = "paper_cache/",
               fig.path = "figures/",
               comment = "#>",
               fig.align = 'center', 
               out.width = "70%")

@@

\begin{tcolorbox}[width=\textwidth,
                  boxsep=5pt,
                  left=5pt,
                  right=5pt,
                  top=5pt,
                  ]
**Education, Training & Achievement Scores**

@@

**Employment**

@@

**Household, Geography & Contextual Variables**
